Perceptions of Information Disclosure Risks for Wearable Devices

### 2016-01-29 USEC2016-camera-ready/camera-ready.tex
change title and abstract to discuss information disclosure

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Risk Perceptions for Wearable Devices}

@@

\begin{abstract}
\noindent Wearable devices, or ``wearables,'' bring great benefits but also potential risks that could expose users' activities without their awareness or consent. We surveyed 1,782 Internet users about risks associated with the capabilities of popular wearable devices on the market in order to identify risks that users find concerning. Our study relatively ranks a range of potential data capture scenarios enabled by wearable devices, investigates the impact of the recipient of the data on the perceived risk of data capture, and explores the landscape of users' concerns associated with wearable devices (including privacy and security, but also including factors such as increased safety risk, changes in social behaviors, and how wearable devices are unfashionable). To our knowledge, this is the largest user-based experiment concerning security and privacy concerns regarding wearables. We hope that this work will inform the community about user perceptions of wearable devices and aid in the design of future user notification, permission management, and access control schemes for wearables.
\end{abstract}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Perceptions of Information Disclosure Risks for Wearable Devices}

@@

\begin{abstract}
\noindent Wearable devices, or ``wearables,'' bring great benefits but also potential information disclosure risks that could expose users' activities without their awareness or consent. We surveyed 1,782 Internet users about various data associated with the capabilities of popular wearable devices on the market to identify which users find most concerning if disclosed. Our study relatively ranks a range of potential data capture scenarios enabled by wearable devices, investigates the impact of the recipient of the data on the perceived risk of data disclosure, and concludes with a survey of users' risks perceptions associated with wearable devices. Users perceive associate risks of owning a wearable with compromised privacy and security, but also consider factors such as safety risk, changes in social behaviors, and how wearable devices are unfashionable. To our knowledge, this is the largest user-based experiment concerning information disclosure regarding wearables. We hope that this work will aid in the design of future user notification, permission management, and access control schemes for wearables.
\end{abstract}
